Flat-histogram method comparison on the 2D Ising model

### 2020-06-22 ising/referee-response.md

Dear editor,

We appreciate the referees' careful reading of our paper, and feel that their
feedback has led to a significant improvement. We have addressed all of the
first referee's comments by added two paragraphs to the introduction and a
section in the paper to 'Address the general problem of all "flat-histogram"
methods'. We also strengthen the abstract to address the concerns raised by the
second referee. We point out that: (i) Our paper is the first of its kind (to
the best of our knowledge) to compare ``production run'' WL with other recent
flat-histogram methods. (ii) It is important to test SAD's convergence
properties on the 2D Ising where the range of energies is easily known (thus
biasing in favor of WL methods). ...

### 2020-06-22 ising/ising-body.tex
a few suggestions on ising edit

Nadler \emph{et al.} and Trebst \emph{et al.} systematically examined optimized
ensembles due to performance issues flat-histogram methods faced when
confronted with hidden energy barriers~\cite{nadler2007generalized,
nadler2007dynamics, trebst2004optimizing}. Trebst \emph{et al.} used their
optimized ensemble to systematically set the temperature range(s) and
implemented an optimized replica-exchange~\cite{trebst2006optimized}.
Replica-exchange Wang-Landau has been developed with great
success~\cite{perera2016magnetic} and adapting flat-histogram methods to use
such an optimized ensemble is doable

@@

>>>>

\davidsays{let's keep replica exchange and optimized ensemble in separate paragraphs}

Nadler \emph{et al.} and Trebst \emph{et al.} systematically examined optimized
ensembles due to performance issues flat-histogram methods faced when
confronted with hidden energy barriers~\cite{nadler2007generalized,
nadler2007dynamics, trebst2004optimizing}. Trebst \emph{et al.} used their
optimized ensemble to systematically set the temperature range(s) and
implemented an optimized replica-exchange~\cite{trebst2006optimized}
\davidsays{looks like this is not a flat-histogram approach, scrap this reference}.

@@

Replica exchange Wang-Landau (REWL) was introduced \davidsays{Need to discuss this, and each of these algorithms
are sufficiently similar that this approach should apply to them.}\cite{vogel2013rewl}.
Replica-exchange Wang-Landau has been developed with great
success~\cite{perera2016magnetic} and adapting flat-histogram methods to use
such an optimized ensemble is doable
